---
title: "HN AltModel 20220127"
author: "LaurenErdman"
date: "27/01/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4 
    number_sections: true
    code_folding: hide
---

# Alternative model 
```{r setup, include=FALSE}


library(readxl)
library(reshape2)
library(rjson)
library(RJSONIO)
library(V8)
library(ggplot2)
library(umap)


results_wd = paste(c(strsplit(x = getwd(), split = "/")[[1]][1:(length(strsplit(x = getwd(), split = "/")[[1]])-3)], "Results_20220126"), collapse = "/")
results_wd = paste0(results_wd, "/")

### FUNCTIONS

get_hn_only = function(in_df){
  left_df = in_df[in_df$Side == 1 & in_df$view_side == "Left",]
  right_df = in_df[in_df$Side == 2 & in_df$view_side == "Right",]
  both_df = in_df[in_df$Side == 3,]
  
  out_df = rbind(left_df, right_df, both_df)
  
  return(out_df)
}

get_sen_spec = function(score_vec, target, threshold){
  score0 = score_vec[target == 0]
  score1 = score_vec[target == 1]
  
  # browser()
  
  tnr = sum(score0 < threshold)/length(score0)
  fnr = sum(score1 < threshold)/length(score1)
  
  out_list = list("specificity" = list("est" = tnr),
                  "sensitivity" = list("est" = 1-fnr))
  return(out_list)
}


get_auroc_aurpc = function(score_vec, target, n_it=1000){
  
  require(EGAD)
  require(pROC)
  
  # browser()
  
  
  ### BREAKING HERE WITH NA's
  # target = na.omit(target)
  # score_vec = na.omit(score_vec)
  # target = target[!is.na(target)]
  # score_vec = score_vec[!is.na(score_vec)]
  # cat(target)
  # cat("\n")
  # cat(score_vec)
  # cat("\n")
    
  sample_size = length(score_vec)
  
  ## AUPRC
  
  auprc_stat = ifelse(length(na.omit(unique(target))) == 2, auprc(score_vec, target), NA)
  
  auprc_samples = sapply(1:n_it, function(i){
    set.seed(i)
    
    my_samp = sample.int(n = sample_size, size = sample_size, replace = TRUE)
    
    auprc_samp = ifelse(length(na.omit(unique(target[my_samp]))) == 2, auprc(score_vec[my_samp], target[my_samp]), NA)
    
    return(auprc_samp)
  })
  
  auprc_ci = quantile(sort(auprc_samples),c(0.025, 0.975))
  
  ## AUROC
  
  auroc_stat = ifelse(length(na.omit(unique(target))) == 2, auc(roc(target, score_vec,quiet = TRUE)), NA)
  
  auroc_samples = sapply(1:n_it, function(i){
    set.seed(i)
    
    my_samp = sample.int(n = sample_size, size = sample_size, replace = TRUE)

    auroc_samp = ifelse(length(na.omit(unique(target[my_samp]))) == 2,auc(roc(target[my_samp], score_vec[my_samp],quiet = TRUE)), NA)

    return(auroc_samp)    
  })

  auroc_ci = quantile(sort(auroc_samples),c(0.025, 0.975))

  ## RETURN ALL STATS
    
  out_list = list("auprc" = auprc_stat,
                  "auprc_ci" = auprc_ci,
                  "auroc" = auroc_stat,
                  "auroc_ci" = auroc_ci)  
  return(out_list)
}


auroc_auprc_split = function(score_vec, target, split_vec, n_it=1000){
  
  out_list = list()
  
  # browser()
  
  for(grp in na.omit(unique(split_vec))){
    
    sub_score = na.omit(score_vec[split_vec == grp])
    sub_target = na.omit(target[split_vec == grp])
    
    if(length(na.omit(unique(sub_target))) == 2){
      out_list[[grp]] = get_auroc_aurpc(score_vec = sub_score, target = sub_target, n_it=n_it)
    } else{
      out_list[[grp]] = NA
    }

        
  }

  return(out_list)  
}

get_sen_spec_withCI = function(score_vec, target, threshold, n_it, out_vecs=FALSE){
  
  out_list = get_sen_spec(score_vec=score_vec,
                          target=target,
                          threshold=threshold)
  n = length(score_vec)
  
  sen_vec = c()
  spec_vec = c()
  for(i in 1:n_it){
    set.seed(i)
    
    # browser()
    samp = sample(1:n,size = n,replace = TRUE)
    true_tnr_fnr = get_sen_spec(score_vec=score_vec[samp],
                                target=target[samp],
                                threshold=threshold)
    sen_vec = c(sen_vec, true_tnr_fnr$sensitivity)
    spec_vec = c(spec_vec, true_tnr_fnr$specificity)
  }
  
  # browser()
  sen_vec = sort(unlist(sen_vec))
  spec_vec = sort(unlist(spec_vec))
  
  out_list[["sensitivity"]][["ci"]] = quantile(sen_vec,c(0.025, 0.975))
  out_list[["specificity"]][["ci"]] = quantile(spec_vec,c(0.025, 0.975))
  
  if(out_vecs){
    
    out_list[["sensitivity"]][["vec"]] = c(sen_vec, rep(NA, n_it - length(sen_vec)))
    out_list[["specificity"]][["vec"]] = c(spec_vec, rep(NA, n_it - length(spec_vec)))
    
    
  }
  
  return(out_list)
  
}  

sen_spec_split = function(score_vec, target, split_vec, threshold, n_it, out_vecs=FALSE){
  split_vals = unique(split_vec)
  
  out_list = list()
  
  for(split_val in split_vals){
    
    # browser()
    
    split_score = na.omit(score_vec[split_vec == split_val])
    split_target = na.omit(target[split_vec == split_val])
    
    out_list[[split_val]] = get_sen_spec_withCI(score_vec = split_score, 
                                                target = split_target, 
                                                threshold = threshold, 
                                                n_it = n_it, 
                                                out_vecs = out_vecs)
  }
  
  return(out_list)  
}

find_sensitivity_thresh = function(pred, label, sensitivity = 0.95){
  sorted_lab = label[order(pred, decreasing = FALSE)]
  sorted_pred = sort(pred, decreasing = FALSE)
  n = length(sorted_lab)

  sen = sapply(1:length(sorted_lab), function(i){
    return(sum(sorted_lab[i:n])/sum(sorted_lab))
  })

  sen_enough = sen[sen > sensitivity]
  threshold = sorted_pred[length(sen_enough)]

  return(threshold)
}

get_fnrs = function(in_list, sensitivity = 0.95, thresh_set_split = "val",
                    epoch = 47, test_sub = NULL, n_its = 500, fold = 1, st=TRUE, stan=TRUE,
                    return_threshold=FALSE){

  # browser()

  train_pred = in_list$train[[fold]][[epoch]][["pred"]]
  train_label = in_list$train[[fold]][[epoch]][["target"]]

  val_pred = in_list$val[[fold]][[epoch]][["pred"]]
  val_label = in_list$val[[fold]][[epoch]][["target"]]

  if(is.null(test_sub)){
    test_pred = in_list$test[[fold]][[epoch]][["pred"]]
    test_label = in_list$test[[fold]][[epoch]][["target"]]
  } else{
    test_pred = in_list$test[[fold]][[epoch]][["pred"]][in_list$test[[fold]][[epoch]][["id"]] %in% test_sub]
    test_label = in_list$test[[fold]][[epoch]][["target"]][in_list$test[[fold]][[epoch]][["id"]] %in% test_sub]
  }


  threshold = find_sensitivity_thresh(pred = in_list[[thresh_set_split]][[fold]][[epoch]][["pred"]],
                                      label = in_list[[thresh_set_split]][[fold]][[epoch]][["target"]],
                                      sensitivity = sensitivity)

  # print(paste0(thresh_set_split, " threshold for epoch ", epoch, " fold ", fold, ": ", threshold))

  train_fnr = sum(train_label[train_pred < threshold])/sum(train_label)
  val_fnr = sum(val_label[val_pred < threshold])/sum(val_label)
  test_fnr = sum(test_label[test_pred < threshold])/sum(test_label)

  out_list = list("train" = list("fnr" = train_fnr),
                  "val" = list("fnr" = val_fnr),
                  "test" = list("fnr" = test_fnr))
  train_fnrs = c()
  val_fnrs = c()
  test_fnrs = c()

  if(st){
    st_pred = in_list$st[[fold]][[epoch]][["pred"]]
    st_label = in_list$st[[fold]][[epoch]][["target"]]
    st_fnr = sum(st_label[st_pred < threshold])/sum(st_label)
    out_list[["st"]] = list("fnr" = st_fnr)
    st_fnrs = c()
  }
  if(stan){
    stan_pred = in_list$stan[[fold]][[epoch]][["pred"]]
    stan_label = in_list$stan[[fold]][[epoch]][["target"]]
    stan_fnr = sum(stan_label[stan_pred < threshold])/sum(stan_label)
    out_list[["stan"]] = list("fnr" = stan_fnr)
    stan_fnrs = c()
  }

  for(it in 1:n_its){

    train_sample = sample(1:length(train_pred),size = length(train_pred), replace = TRUE)
    val_sample = sample(1:length(val_pred),size = length(val_pred), replace = TRUE)
    test_sample = sample(1:length(test_pred),size = length(test_pred), replace = TRUE)

    train_pred_s = train_pred[train_sample]
    train_label_s = train_label[train_sample]

    val_pred_s = val_pred[val_sample]
    val_label_s = val_label[val_sample]

    test_pred_s = test_pred[test_sample]
    test_label_s = test_label[test_sample]

    train_fnrs = c(sum(train_label_s[train_pred_s < threshold])/sum(train_label_s), train_fnrs)
    val_fnrs = c(sum(val_label_s[val_pred_s < threshold])/sum(val_label_s), val_fnrs)
    test_fnrs = c(sum(test_label_s[test_pred_s < threshold])/sum(test_label_s), test_fnrs)

    if(st){
      st_sample = sample(1:length(st_pred),size = length(st_pred), replace = TRUE)
      st_pred_s = st_pred[st_sample]
      st_label_s = st_label[st_sample]
      st_fnrs = c(sum(st_label_s[st_pred_s < threshold])/sum(st_label_s), st_fnrs)
    }
    if(stan){
      stan_sample = sample(1:length(stan_pred),size = length(stan_pred), replace = TRUE)
      stan_pred_s = stan_pred[stan_sample]
      stan_label_s = stan_label[stan_sample]
      stan_fnrs = c(sum(stan_label_s[stan_pred_s < threshold])/sum(stan_label_s), stan_fnrs)
    }

  }

  train_fnrs = sort(train_fnrs)
  val_fnrs = sort(val_fnrs)
  test_fnrs = sort(test_fnrs)

  out_list[["train"]][["ci"]] = quantile(train_fnrs, c(0.025, 0.975))
  out_list[["val"]][["ci"]] = quantile(val_fnrs, c(0.025, 0.975))
  out_list[["test"]][["ci"]] = quantile(test_fnrs, c(0.025, 0.975))

  if(st){
    out_list[["st"]][["ci"]] = quantile(st_fnrs, c(0.025, 0.975))
  }
  if(stan){
    out_list[["stan"]][["ci"]] = quantile(stan_fnrs, c(0.025, 0.975))
  }

  if(return_threshold){
    return(threshold)
  } else{
    return(out_list)
  }
}

add_platt_preds_dprep = function(in_list, scale_ref = "val", epoch = 1,
                           sensitivity = 0.95, verbose=TRUE){
  in_list_names = names(in_list)
  
  if("prenatal" %in% in_list_names){
    in_list[["prenatal"]] = NULL
  }
  in_list_names = names(in_list)
  
  to_scale = in_list_names[in_list_names != scale_ref]

  folds = length(in_list[[scale_ref]])

  ## creating and applying scaling model
  for(fold in 1:folds){

    threshold = get_fnrs(in_list = in_list, epoch = epoch,fold = fold, return_threshold=TRUE,sensitivity = sensitivity)

    # browser()

    scale_set = data.frame(label = in_list[[scale_ref]][[fold]][[epoch]][["target"]],
                           pred = in_list[[scale_ref]][[fold]][[epoch]][["pred"]])

    scale_mod = glm(label ~ pred, scale_set, family = binomial)

    if(verbose){
      print(summary(scale_mod))
    }

    in_list[[scale_ref]][[fold]][[epoch]][["pred_scaled"]] = predict(scale_mod, newdata = data.frame(pred = in_list[[scale_ref]][[fold]][[epoch]][["pred"]]),type = "response")
    in_list[[scale_ref]][[fold]][[epoch]][["threshold"]] = predict(scale_mod, newdata = data.frame(pred = threshold), type = "response")

    for(group in to_scale){
      in_list[[group]][[fold]][[epoch]][["pred_scaled"]] = predict(scale_mod, newdata = data.frame(pred = in_list[[group]][[fold]][[epoch]][["pred"]]),type = "response")
    }
  }

  # browser()

  return(in_list)
}


add_platt_preds = function(in_list, scale_ref = "val", epoch = 1){
  in_list_names = names(in_list)
  to_scale = in_list_names[in_list_names != scale_ref]
  
  folds = length(in_list[[scale_ref]])
  
  ## creating and applying scaling model
  for(fold in 1:folds){
    
    threshold = get_fnrs(in_list = in_list, epoch = epoch,fold = fold, return_threshold=TRUE)
    
    # browser()
    
    scale_set = data.frame(label = in_list[[scale_ref]][[fold]][[epoch]][["target"]], 
                           pred = in_list[[scale_ref]][[fold]][[epoch]][["pred"]])
    
    scale_mod = glm(label ~ pred, scale_set, family = binomial)    
    
    in_list[[scale_ref]][[fold]][[epoch]][["pred_scaled"]] = predict(scale_mod, newdata = data.frame(pred = in_list[[scale_ref]][[fold]][[epoch]][["pred"]]),type = "response")
    in_list[[scale_ref]][[fold]][[epoch]][["threshold"]] = predict(scale_mod, newdata = data.frame(pred = threshold), type = "response")
    
    for(group in to_scale){
      in_list[[group]][[fold]][[epoch]][["pred_scaled"]] = predict(scale_mod, newdata = data.frame(pred = in_list[[group]][[fold]][[epoch]][["pred"]]),type = "response")
    }
  }  
  
  # browser()
  
  return(in_list)
}

get_most_recent = function(in_dataset){
  
  # browser() 
  # if(!("USNumber" %in% names(in_dataset))){
  #   in_dataset$USNumber = labels(in_dataset$US_num
  # }
  # 
  out_dataset = data.frame(matrix(nrow = 0, ncol = ncol(in_dataset)))
  names(out_dataset) = names(in_dataset)
  
  for(id in unique(in_dataset$pt_id)){
    pt_df = in_dataset[in_dataset$pt_id == id, ]
    max_row = pt_df[pt_df$USNumber == max(as.numeric(pt_df$USNumber)),][1,]
    
    out_dataset = rbind(out_dataset,max_row)
  }
  
  names(out_dataset) = names(in_dataset) 
  
  return(out_dataset)
}

make_st_df = function(st_df, st_details){

  # browser()
  
  st_details$STID = paste0("STID", st_details$ID, "_", st_details$view_side, "_", st_details$US_num, "_1")
  
  st_merged = merge(st_df, st_details, by.x = "id", by.y = "STID")
  head(st_merged)
  st_merged$pt_id = unlist(lapply(strsplit(as.character(st_merged$id),"_"),function(x){x[1]}))
  length(unique(st_merged$pt_id))
  
  st_uniq = st_merged[!duplicated(st_merged$ID),]
  table(st_uniq$target)
  
  ## confirming HN only 
  st_hn_only = get_hn_only(in_df = st_merged)
  
  st_hn_only$id_num = as.numeric(substr(st_hn_only$id,5,7))
  
  st_hn_only$sex = factor(st_hn_only$Sex, levels = c(1,2), labels = c("male","female"))
  
  if(!("target01" %in% names(st_hn_only))){
    st_hn_only$target01 = ifelse(st_hn_only$target == "no Obstruction", 0, 1)
  }
  
  st_hn_only$apd_groups = factor(st_hn_only$apd_groups, levels = c("under_6", "apd_6_to_9", "apd_9_to_14", "over_14", "unmeasured"))
  st_hn_only$apd_groups[is.na(st_hn_only$apd_groups)] = "unmeasured"
  st_hn_only$HN_Side_fac = factor(st_hn_only$Side, levels = 1:3, labels = c("Left", "Right", "Both"))
  st_hn_only$USNumber = factor(st_hn_only$US_num, levels = sort(unique(st_hn_only$US_num)))
  
  st_hn_only$age_grps = NA
  st_hn_only$age_grps[st_hn_only$age_at_US_wk < 102] = "under2"
  st_hn_only$age_grps[st_hn_only$age_at_US_wk >= 102 & 
                        st_hn_only$age_at_US_wk < 260] = "age2to5"
  st_hn_only$age_grps[st_hn_only$age_at_US_wk >= 260] = "over5"
  st_hn_only$age_grps_fac = factor(st_hn_only$age_grps, levels = c("under2","age2to5","over5"))
  
  st_hn_only$PostalCode = factor(st_hn_only$PC_region, levels = c("M", "N", "L", "P", "K"))
  
  st_hn_only$prep = ifelse(st_hn_only$id_num <= 300, "prep1", "prep2")
  st_hn_only$prep = factor(st_hn_only$prep, levels = c("prep1","prep2"))
  
  st_hn_only$US_machine[is.na(st_hn_only$US_machine)] = "Unknown"
  
  ### most recent only dataset: 
  hn_only_most_recent = get_most_recent(in_dataset = st_hn_only)
  
  out_list = list("overall" = st_hn_only,"most_recent" = hn_only_most_recent)
  
  return(out_list)
}



make_stan_df = function(stan_df, stan_datasheet, stan_train){
  stan_df$target01 = ifelse(stan_df$target == "no Obstruction", 0, 1)
  
  stan_datasheet$img_id = paste0(stan_datasheet$anon_mrn,"_",stan_datasheet$`side of hydronephrosis`,"_",stan_datasheet$anon_accession,"_1")
  
  stan_merge = merge(stan_df, stan_datasheet, by.x = "id", by.y = "img_id")
  
  stan_uniq = stan_merge[!duplicated(stan_merge$anon_mrn),]
  
  dim(stan_merge)
  
  stan_merge$age_grps = NA
  stan_merge$age_grps[stan_merge$age < 2] = "under2"
  stan_merge$age_grps[stan_merge$age >= 2 & stan_merge$age <= 5] = "age2to5"
  stan_merge$age_grps[stan_merge$age > 5] = "over5"
  
  stan40_test = stan_merge[!(stan_merge$anon_mrn %in% stan_train),]
    
  out_list = list("overall" = stan_merge, "test40" = stan40_test)
  
  return(out_list)
}




make_uiowa_df = function(ui_df, ui_datasheet, ui_train){
  ui_df$pt_id = unlist(lapply(strsplit(as.character(ui_df$id),"_"),function(x){x[1]}))
  ui_df$target01 = ifelse(ui_df$target == "no Obstruction", 0, 1)
  
  ui_merge = merge(ui_df, ui_datasheet, by.y = "Name", by.x = "pt_id")
  
  ui_merge$age_days = difftime(ui_merge$Ultrasound.Date, ui_merge$DOB, units = "days")
  
  ui_merge$age_grp = NA
  ui_merge$age_grp[ui_merge$age_days < 365*2] = "under2"
  ui_merge$age_grp[ui_merge$age_days >= 365*2 & ui_merge$age_days <= 365*5] = "age2to5"
  ui_merge$age_grp[ui_merge$age_days > 365*5] = "over5"
  
  ui40_test = ui_merge[!(ui_merge$pt_id %in% ui_train),]
  
  out_list = list("overall" = ui_merge, "test40" = ui40_test)
  
  return(out_list)
}



```


```{r}

print(results_wd)

```


# Original SickKids model
```{r silent_trial_data, warning=FALSE, include = FALSE}
###
###     SILENT TRIAL DATA 
###

SENSITIVITY = 0.90

## No test data -- model usedto test Stanford and Silent trial
# raw_in = readLines(paste0(results_wd,"NoFinalLayerFineTuneSickKidsTrained_noSTContra_TrainOnly_40epochs_bs16_lr0.001_RCFalse_covTrue_OSFalse.json"))
raw_in = readLines(paste0(results_wd,"/AltModel/NoFinalLayerFineTuneSickKidsTrained_AltModel_TrainOnly_40epochs_bs16_lr0.001_RCFalse_covTrue_OSFalse.json"))
test = v8()
test$assign("dat", JS(raw_in))
st_stan_test = test$get("dat")

st_stan_test = add_platt_preds_dprep(in_list = st_stan_test, epoch = 30,sensitivity = SENSITIVITY, verbose = FALSE)

st_preds = data.frame(st_pred_mod_ep30 = st_stan_test$st[[1]][[30]]$pred_scaled,
                      id = st_stan_test$st[[1]][[30]]$id,
                      target01 = st_stan_test$st[[1]][[30]]$target)
st_preds$target = factor(st_preds$target01, levels = c(0,1), labels = c("no Obstruction", "Obstruction"))
# head(st_preds)

fold=1
thresh_ep30 = st_stan_test[["val"]][[fold]][[30]][["threshold"]]

st_orig_list = make_st_df(st_df = st_preds,
                          st_details = read.csv(paste0(results_wd, "/Datasheets/SilentTrial_Datasheet_deID_20211205.csv"),header = TRUE, as.is = TRUE))

st_hn_only = st_orig_list[["overall"]]
hn_only_most_recent = st_orig_list[["most_recent"]]

####
#### SILENT TRIAL ALL VISITS
####



####
#### SILENT TRIAL MOST-RECENT ONLY 
####



```

#### Model performance 
##### Overall 
```{r}

## overall 
cat("All silent trial participant ultrasounds overall model performance")
get_auroc_aurpc(score_vec = st_hn_only$st_pred_mod_ep30, 
                           target = st_hn_only$target01)

(st_overall_origmod = get_sen_spec_withCI(score_vec = st_hn_only$st_pred_mod_ep30, 
                                         target = st_hn_only$target01, 
                                         threshold = thresh_ep30, 
                                         n_it = 500, out_vecs = FALSE))




```

##### By preparation
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$prep, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By ApD
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$apd_groups, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By HN side
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$Side, 
               threshold = thresh_ep30, 
               n_it = 500)
```

#### By Kidney side
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$view_side, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By Age 
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$age_grps_fac, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By Postal code 
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$PostalCode, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By US Number
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$USNumber, 
               threshold = thresh_ep30, 
               n_it = 500)

```

#### By US machine 
```{r}
sen_spec_split(score_vec = st_hn_only$st_pred_mod_ep30, 
               target = st_hn_only$target01, 
               split_vec = st_hn_only$US_machine, 
               threshold = thresh_ep30, 
               n_it = 500)

```



### SickKids silent trial data: Most recent visits only

#### Model performance: Most recent observations only 
##### Overall
```{r}

####
#### SILENT TRIAL MOST-RECENT ONLY 
####

get_auroc_aurpc(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                           target = hn_only_most_recent$target01)

(st_mostrec_origmod = get_sen_spec_withCI(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                                         target = hn_only_most_recent$target01, 
                                         threshold = thresh_ep30, 
                                         n_it = 500, out_vecs = FALSE))

```

##### By prepartion method
```{r}
auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$prep, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$prep, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Sex
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$sex, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$sex, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By ApD Group
```{r}
auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$apd_groups, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$apd_groups, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By HN side
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$Side, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$Side, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Kidney side
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$view_side, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$view_side, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Age
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$age_grps_fac, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$age_grps_fac, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Postal code 
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$PostalCode, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$PostalCode, 
               threshold = thresh_ep30, 
               n_it = 500)
```

##### By Ultrasound number
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$USNumber, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$USNumber, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Ultrasound machine 
```{r}

auroc_auprc_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
                  target = hn_only_most_recent$target01, 
                  split_vec = hn_only_most_recent$US_machine, 
                  n_it=500)

sen_spec_split(score_vec = hn_only_most_recent$st_pred_mod_ep30, 
               target = hn_only_most_recent$target01, 
               split_vec = hn_only_most_recent$US_machine, 
               threshold = thresh_ep30, 
               n_it = 500)
```

### Stanford original model performance
```{r, include=FALSE}
stan_preds = data.frame(stan_pred_mod_ep30 = st_stan_test$stan[[1]][[30]]$pred_scaled,
                      id = st_stan_test$stan[[1]][[30]]$id,
                      target01 = st_stan_test$stan[[1]][[30]]$target)
stan_preds$target = factor(stan_preds$target01, levels = c(0,1), labels = c("no Obstruction", "Obstruction"))
stan_df = stan_preds
stan_datasheet = read_excel(paste0(results_wd,"/Datasheets/AI Hydronephrosis Data deidentified.xlsx"))

stan_orig_list = make_stan_df(stan_df = stan_df,
             stan_datasheet = read_excel(paste0(results_wd,"/Datasheets/AI Hydronephrosis Data deidentified.xlsx")),
             stan_train = readRDS(paste0(results_wd,"/Datasheets/Stan60%train_ids_20220114.rds")))


stan_merge = stan_orig_list[["overall"]]
head(stan_merge)
stan40_test = stan_orig_list[["test40"]]

dim(stan_merge)


dim(stan40_test)



```

#### Demographics 
```{r}

# Overall
table(stan_merge$target)

# Unique patients overall
table(stan_merge$target[!duplicated(stan_merge$anon_mrn)])

##HN Side
table(stan_merge$`side of hydronephrosis`)
table(stan_merge$`side of hydronephrosis`,stan_merge$target)

# Sex
table(stan_merge$sex)
table(stan_merge$target, stan_merge$sex)

# Age
table(stan_merge$age_grps)
table(stan_merge$age_grps, stan_merge$target)


```


#### Model performance
```{r}

get_auroc_aurpc(score_vec = stan_df$stan_pred_mod_ep30, 
                    target = stan_preds$target01)

(stan_all_origmod = get_sen_spec_withCI(score_vec = stan_df$stan_pred_mod_ep30, 
                    target = stan_preds$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))


```


```{r}

get_auroc_aurpc(score_vec = stan40_test$stan_pred_mod_ep30, 
                    target = stan40_test$target01)

(stan_40test_origmod = get_sen_spec_withCI(score_vec = stan40_test$stan_pred_mod_ep30, 
                    target = stan40_test$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))

```




##### By sex 
```{r}

auroc_auprc_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$sex, 
                  n_it=500)

sen_spec_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$sex, 
               threshold = thresh_ep30, 
               n_it = 500)
```


##### By side
```{r}

auroc_auprc_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$`side of hydronephrosis`, 
                  n_it=500)

sen_spec_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$`side of hydronephrosis`, 
               threshold = thresh_ep30, 
               n_it = 500)

```


##### By Age
```{r}
auroc_auprc_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$age_grps, 
                  n_it=500)

sen_spec_split(score_vec = stan_merge$stan_pred_mod_ep30, 
               target = stan_merge$target01, 
               split_vec = stan_merge$age_grps, 
               threshold = thresh_ep30, 
               n_it = 500)

```


### UIowa original model performance
```{r, include=FALSE}

ui_preds = data.frame(ui_pred_mod_ep30 = st_stan_test$ui[[1]][[30]]$pred_scaled,
                        id = st_stan_test$ui[[1]][[30]]$id,
                        target = st_stan_test$ui[[1]][[30]]$target)

ui_preds$target = factor(ui_preds$target, levels = c(0,1), labels = c("no Obstruction", "Obstruction"))
ui_df = ui_preds

ui_datasheet = read.csv(paste0(results_wd,"/Datasheets/UIowa_DeID_Datasheet.csv"), header = TRUE, as.is = TRUE)
names(ui_datasheet)[1] = "Name"

ui_df$pt_id = unlist(lapply(strsplit(as.character(ui_df$id),"_"),function(x){x[1]}))
ui_df$target01 = ifelse(ui_df$target == "no Obstruction", 0, 1)

ui_merge = merge(ui_df, ui_datasheet, by.y = "Name", by.x = "pt_id")

ui_merge$age_days = ui_merge$Age_days

ui_merge$age_grp = NA
ui_merge$age_grp[ui_merge$age_days < 365*2] = "under2"
ui_merge$age_grp[ui_merge$age_days >= 365*2 & ui_merge$age_days <= 365*5] = "age2to5"
ui_merge$age_grp[ui_merge$age_days > 365*5] = "over5"

ui_train = readRDS(paste0(results_wd, "/Datasheets/UI60%train_ids_20220114.rds"))

ui40_test = ui_merge[!(ui_merge$pt_id %in% ui_train),]

```

#### Model performance 

##### Overall
```{r}

get_auroc_aurpc(score_vec = ui_df$ui_pred_mod_ep30, 
                    target = ui_df$target01)

(ui_all_origmod = get_sen_spec_withCI(score_vec = ui_df$ui_pred_mod_ep30, 
                    target = ui_df$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))

```

###### 40% Test
```{r}

get_auroc_aurpc(score_vec = ui40_test$ui_pred_mod_ep30, 
                    target = ui40_test$target01)

(ui_40test_origmod = get_sen_spec_withCI(score_vec = ui40_test$ui_pred_mod_ep30, 
                    target = ui40_test$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))

```

##### By Sex
```{r}

auroc_auprc_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$Gender, 
                  n_it=500)

sen_spec_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$Gender, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By HN Side
```{r}
auroc_auprc_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$U.B, 
                  n_it=500)

sen_spec_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$U.B, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Age Group
```{r}

auroc_auprc_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$age_grp, 
                  n_it=500)

sen_spec_split(score_vec = ui_merge$ui_pred_mod_ep30, 
               target = ui_merge$target01, 
               split_vec = ui_merge$age_grp, 
               threshold = thresh_ep30, 
               n_it = 500)

```


### CHOP original model performance
```{r}

chop_preds = data.frame(chop_pred_mod_ep30 = st_stan_test$chop[[1]][[30]]$pred_scaled,
                        id = st_stan_test$chop[[1]][[30]]$id,
                        target = st_stan_test$chop[[1]][[30]]$target)

chop_preds$target = factor(chop_preds$target, levels = c(0,1), labels = c("no Obstruction", "Obstruction"))
chop_df = chop_preds

chop_datasheet = read.csv(paste0(results_wd,"/Datasheets/CHOP_deid_20220127.csv"), header = TRUE, as.is = TRUE)
names(chop_datasheet)[1] = "Name"

chop_df$pt_id = unlist(lapply(strsplit(as.character(chop_df$id),"_"),function(x){x[1]}))
chop_df$pt_id = sub(pattern = "CHOP",replacement = "",chop_df$pt_id)
chop_df$target01 = ifelse(chop_df$target == "no Obstruction", 0, 1)

chop_merge = merge(chop_df, chop_datasheet, by.y = "Name", by.x = "pt_id")

chop_merge$age_days = as.numeric(chop_merge$Age.of.patient.at.US..weeks.)*7

chop_merge$age_grp = NA
chop_merge$age_grp[chop_merge$age_days < 365*2] = "under2"
chop_merge$age_grp[chop_merge$age_days >= 365*2 & chop_merge$age_days <= 365*5] = "age2to5"
chop_merge$age_grp[chop_merge$age_days > 365*5] = "over5"

chop_train = readRDS(paste0(results_wd, "/Datasheets/CHOP60%train_ids_20220114.rds"))
chop_train = sub(pattern = "CHOP",replacement = "",x = chop_train)

chop40_test = chop_merge[!(chop_merge$pt_id %in% chop_train),]

```

#### Model performance 

##### Overall 
```{r}

get_auroc_aurpc(score_vec = chop_df$chop_pred_mod_ep30, 
                    target = chop_df$target01)

(chop_all_origmod = get_sen_spec_withCI(score_vec = chop_df$chop_pred_mod_ep30, 
                    target = chop_df$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))

```

###### 40% Test 
```{r}

get_auroc_aurpc(score_vec = chop40_test$chop_pred_mod_ep30, 
                    target = chop40_test$target01)

(chop_40test_origmod = get_sen_spec_withCI(score_vec = chop40_test$chop_pred_mod_ep30, 
                    target = chop40_test$target01, 
                    threshold = thresh_ep30, 
                    n_it = 500))

```

##### By Sex
```{r}
auroc_auprc_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$Sex, 
                  n_it=500)

sen_spec_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$Sex, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By HN Side
```{r}

auroc_auprc_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$Laterality.of.hydro, 
                  n_it=500)

sen_spec_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$Laterality.of.hydro, 
               threshold = thresh_ep30, 
               n_it = 500)

```

##### By Age Group
```{r}

auroc_auprc_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$age_grp, 
                  n_it=500)

sen_spec_split(score_vec = chop_merge$chop_pred_mod_ep30, 
               target = chop_merge$target01, 
               split_vec = chop_merge$age_grp, 
               threshold = thresh_ep30, 
               n_it = 500)

```
